Polarized Cubical Types

### 2014-05-22 ring.tex
comment on 2d

We first define the syntax a semantic model of types and then discuss type
isomorphisms.

@@

\begin{verbatim}
A critical isomorphism that is 
not reflected at all in the semantics
is that 1-1 = 0

>>>>

We first define the syntax and then present a simple semantic model of types
which is then refined.

@@

\begin{verbatim}
So the story is that as we are building
the denotations of types, we add these
paths making up the cubes. The only
case where we add new paths is multiplication
(see Fig.1 again). We take the paths p in S1
and the paths q in S2 and build paths (p,q)
in the product space.

Once we have this structure, we do this 
homotopy completion which turns our inductive
type into a higher-inductive type. We 
start adding 2-paths between any path 
connecting (S-S) and the refl path on 0.

Technically this is a functor between (S-S) 
and the empty type mapping S to 0, the 
other S to 0, and the path between them
to refl.

Now consider (a-b)-(c-c). We have a 
functor to (a-b)-0 that contracts the
path between c and -c. We want to 
reduce the dimension of that space
and map to (a-b).

original space

    c ------ c
    |        |  
p1  |        | p2
    |        |  
    a ------ b
       p3

after collapsing the two c's

      0
     /\
    /  \
   a -- b

or because path compose

  a ---- b
    ----

where the top path is p1;p2
and the bottom path is p3

I think we should have a 2-path
between them to say that these
paths are equivalent which will 
then collapse the square to a 
line as desired.

A critical isomorphism that is 
not reflected at all in the semantics
is that 1-1 = 0
